---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/risktoollib/RTLappDynamics/workflows/R-CMD-check/badge.svg)](https://github.com/risktoollib/RTLappDynamics/actions)
[![Codecov test coverage](https://codecov.io/gh/risktoollib/RTLappDynamics/branch/master/graph/badge.svg)](https://app.codecov.io/gh/risktoollib/RTLappDynamics?branch=master)
<!-- badges: end -->

***Part of a series of Shiny applications to support education of risk managers and trading analysts in Universities and commodity-trading enterprise.***

# Goals

This appl

The goal of RTLappDynamics


## Installation

You can install the development version of RTLappDynamics from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("risktoollib/RTLappDynamics")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(RTLappDynamics)
RTLappDynamics::run_app()
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.
